Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2024-04-14 LaTeX_paper/paper.tex
Fix title
fix typo

  \vspace{2 cm} 
  \Large\textsc{Final Dissertation\\} 
  \vspace{1 cm} 
  \Huge\textsc{Title\\}
  \Large{\it{Use Of Jigsaw Puzzle Solving Algorithms In The Real World}}

@@

\subsubsection{Basic Components}
To implement the algorithm two fundamental object are defined
\begin{itemize}
  \item \texttt{SinglePiece}: which contains information about a single puzzle piece.
  \item P\texttt{PieceGroup\(<\)T\(>\)} where \texttt{T} can be either a \texttt{PieceGroup} or a \texttt{SinglePiece}\newline
  This element encompasses four elements of type \texttt{T}, each with its own position (top right, top left, bottom left, bottom right).
\end{itemize}
Both \texttt{SinglePiece} and \texttt{PieceGroup} have an ``orientation'' attribute that goes from 0 to 3, this attribute
represent the orientation of the piece, as shown in~\cref{fig:orientation}.
\begin{figure}[H]
  \caption{orientation attribute of an object}\label{fig:orientation}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/orientation.png}
\end{figure}

>>>>

  \vspace{2 cm} 
  \Large\textsc{Final Dissertation\\} 
  \vspace{1 cm} 
  \Huge\textsc{Use Of Jigsaw Puzzle Solving Algorithms In The Real World}

@@

\subsubsection{Basic Components}
To implement the algorithm two fundamental object are defined
\begin{itemize}
  \item \texttt{SinglePiece}: which contains information about a single puzzle piece.
  \item \texttt{PieceGroup\(<\)T\(>\)} where \texttt{T} can be either a \texttt{PieceGroup} or a \texttt{SinglePiece}\newline
  This element encompasses four elements of type \texttt{T}, each with its own position (top right, top left, bottom left, bottom right).
\end{itemize}
Both \texttt{SinglePiece} and \texttt{PieceGroup} have an ``orientation'' attribute that goes from 0 to 3, this attribute
represent the orientation of the piece, as shown in~\cref{fig:orientation}.
\begin{figure}[H]
  \caption{orientation attribute of an object}\label{fig:orientation}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/orientation.png}
\end{figure}
